EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-06-01 06_conclusions_acknowledgement_appendix.tex
v1 + few corrections Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

\section{Conclusions}
We have presented \NAME{}, a versatile, high-performance solver for
generic quantum impurity problems. Leveraging on the massively
parallel algorithms introduced by its predecessor \cite{Amaricci2022CPC}, this version of
the library features new capabilities and symmetries within a unified
framework, providing for instance reliable evaluations of the dynamical correlation
functions of an arbitrary complex frequency.
This makes it particularly well-suited for capturing the
low-energy excitations and complex spectral features of strongly
correlated systems.
We have shown that this new version enables the evaluation of impurity
reduced density matrices directly from Fock space quantities and thus unlocks 
quantum information analyses of correlated systems, an increasingly
essential tool to address emergent phases of quantum materials.

@@

The modular and extensible design of \NAME provides a
natural foundation for future extensions.
For instance to
cluster-DMFT \cite{Capone2004PRB,Kotliar2006RMP,Park2008PRL} where the
impurity problem is generalized to include clusters of interacting
sites. This approach would enable the treatment of spatial
correlations beyond the single-site approximation, capturing effects
such as d-wave pairing in high-temperature superconductors, charge
order, and complex spin textures in strongly correlated systems.
A different outlook is the development of an integration layer with other
quantum embedding methods, such ghost Gutzwiller \cite{Lanata2015PRX},
which heavily rely on solving effective impurity problems.    
We anticipate that \NAME will become a valuable tool for the
computational condensed matter community, supporting a wide range of
studies on strongly correlated materials and providing a reliable
reference platform for quantum impurity solvers.

>>>>

\section{Conclusions}
We have presented \NAME{}, a versatile, high-performance solver for
generic quantum impurity problems. Building on the massively
parallel algorithms introduced by its predecessor \cite{Amaricci2022CPC}, this version of
the library features new capabilities and symmetries within a unified
framework providing, for example, reliable evaluations of the dynamical correlation
functions of an arbitrary complex frequency.
This makes it particularly well-suited for capturing the
low-energy excitations and complex spectral features of strongly
correlated systems.
We have shown that this new version enables the evaluation of impurity
reduced density matrices directly from Fock space quantities and thus enables  
quantum information analysis of correlated systems, which is becoming an essential tool to address emergent phases of quantum materials.

@@

The modular and extensible design of \NAME provides a
natural foundation for future extensions.
For instance it provides a suitable basis to develop cluster-DMFT \cite{Capone2004PRB,Kotliar2006RMP,Park2008PRL} methods, where the
impurity problem is generalized to include clusters of interacting
sites. This approach would enable the treatment of spatial
correlations beyond the single-site approximation, capturing effects
such as d-wave pairing in high-temperature superconductors, charge
order, and complex spin textures in strongly correlated systems.
A different outlook is the development of an integration layer with other
quantum embedding methods, such ghost Gutzwiller \cite{Lanata2015PRX},
which heavily rely on solving effective impurity problems.    
We anticipate that \NAME will become a valuable tool for the
computational condensed matter community, supporting a wide range of
studies on strongly correlated materials and providing a reliable
reference platform for quantum impurity solvers.
